### 2015-07-16 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Fix big in get_model for coupling w Axisem + manual correction

\noindent It generate mesh files (on 1 proc on Curie), and copy files 'list\_gll\_boundary\_spherical.txt' and 'list\_gll\_boundary\_cartesian.txt' in AxiSEM solver dir.

@@

\item[\textbullet] 'iasp91\_dsm' or 'prem\_dsm' : background model used in both AxiSEM ans Specfem3D

@@

\item[\textbullet] Set the file 'Par\_file' with these parmeters :

>>>>

\noindent It generates mesh files (on 1 proc on Curie), and copies files 'list\_gll\_boundary\_spherical.txt' and 'list\_gll\_boundary\_cartesian.txt' in AxiSEM solver dir.

@@

\item[\textbullet] 'iasp91\_dsm' or 'prem\_dsm' : background model used in both AxiSEM and Specfem3D

@@

\item[\textbullet] Set the file 'Par\_file' with these parameters :
